---
title: 'Assignment V: GitHub and the ticketmaster.com API'
subtitle: 'Data Science Project Management | Winter Term 2020 / 2021' 
author: 'Submitted by Lana Kern (Student ID: 5395819)'
date: 'February 16, 2021'
output: 
  html_document:
  toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


I worked together with Michael Lyubkin (Student ID: 4168485), Martin Scheerer (Student ID: 5631373), Anton Höhl (Student ID: 5637078) and Jingwen Xu (Student ID: 5631584). 
I hereby assure that my submission is in line with the *Code of Conduct*  outlined on the lecture slides. 

\

## General setup

Before I present the solutions, I clear my workspace as well as install (if necessary)
and load the packages that are needed throughout the assignment.

```{r general, message=FALSE}
# clear workspace

# Check if needed packages have already been installed. If not, packages are installed. 

# Load packages
```


\

## Exercise 1: Setting up a new GitHub repository

The link to my personal GitHub account where the project's version history is documented is:
`https://github.com/lanakern/DSPM_Assignment5.git`


\

## Exercise 2: Getting to know the API

The most important features and functionalities of the Ticketmaster *Discovery API* for this assignment are:

* The Ticketmaster Discovery API allows one to search for events, attractions, or venues in different countries. 

* The root URL for the *Discover API* is: `https://app.ticketmaster.com/discovery/v2/` where `discovery` denotes the package and `v2` the version.

  + To find all venues the base URL for the `GET()` request is: `https://app.ticketmaster.com/discovery/v2/venues`. 
  
  + This base URL can be expanded by for example specifying the country. 

* To run a successful API call, one needs to pass an API key in the `apikey` query parameter. My retrieved valid API key from the API Explorer is stored in a separate script called `api_key_ticketmaster` in order to comply to the common secrecy practices. 

* The rate limit is 5000 API calls per day and 5 requests per second.

* The API only supports retrieving the 1000th item, i.e. size * page < 1000


\

## Exercise 3: Interacting with the API - the basics


\

## Exercise 4: Interacting with the API - advanced

\

## Exercise 5: Visualizing the extracted data

\

## Exercise 6: Event locations in other countries