---
title: 'Assignment V: GitHub and the ticketmaster.com API'
subtitle: 'Data Science Project Management | Winter Term 2020 / 2021' 
author: 'Submitted by Lana Kern (Student ID: 5395819)'
date: 'February 16, 2021'
output: 
  html_document:
  toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


I worked together with Michael Lyubkin (Student ID: 4168485), Martin Scheerer (Student ID: 5631373), Anton Höhl (Student ID: 5637078) and Jingwen Xu (Student ID: 5631584). 
I hereby assure that my submission is in line with the *Code of Conduct*  outlined on the lecture slides. 

\

## General setup

Before I present the solutions, I clear my workspace as well as install (if necessary)
and load the packages that are needed throughout the assignment.

```{r general, message=FALSE}
# clear workspace
rm(list = ls()) 

# Check if needed packages have already been installed. If not, packages are installed. 
if (!require("httr")) install.packages("httr")  
if (!require("jsonlite")) install.packages("jsonlite") 
if (!require("dplyr")) install.packages("dplyr") 

# Load packages
library(httr)  # for implementing the HTTP methods like GET() in R
library(jsonlite)  # for converting JSON object in R object using fromJSON()
library(dplyr)  # for data manipulation functions
```


\

## Exercise 1: Setting up a new GitHub repository

The link to my personal GitHub account where the project's version history is documented is:
`https://github.com/lanakern/DSPM_Assignment5.git`


\

## Exercise 2: Getting to know the API

The most important features and functionalities of the Ticketmaster *Discovery API* for this assignment are:

* The Ticketmaster Discovery API allows one to search for events, attractions, or venues in different countries. 

* The root URL for the *Discover API* is: `https://app.ticketmaster.com/discovery/v2/` where `discovery` denotes the package and `v2` the version.

  + To find all venues the base URL for the `GET()` request is: `https://app.ticketmaster.com/discovery/v2/venues`. 
  
  + This base URL can be expanded by for example specifying the country. 

* To run a successful API call, one needs to pass an API key in the `apikey` query parameter. My retrieved valid API key from the API Explorer is stored in a separate script called `api_key_ticketmaster.R` in order to comply to the common secrecy practices. The `api_key_ticketmaster.R` is also stored in the R project, but added to the `.gitignore` file so that it is not tracked by GIT. Most importantly, it does not appear in my public GitHub repository. 

* The rate limit is 5000 API calls per day and 5 requests per second.



\

## Exercise 3: Interacting with the API - the basics

The following packages are needed to interact with the APIs using R and already loaded in the *General setup* section:

* The `{httr}` package is a tidyverse package that is needed to implement the HTTP methods in R. It includes functions for the most important http verbs such as `GET()`.

* The `{jsonlite}` package is needed in order to convert a JSON object into a R object by using the provided function `fromJSON()`. 


Next, a first `GET()` request is performed, that searches for event venues in Germany. The following URL is constructed by using the information from Exercise 2, the venue search of the ticketmaster API explorer (*https://developer.ticketmaster.com/api-explorer/v2/*) and the documentation of the venue search (*https://developer.ticketmaster.com/products-and-docs/apis/discovery-api/v2/#search-venues-v2*). 

```{r ex3_first_GET_request}
# load API key into R
source("api_key_ticketmaster.R")

# perform GET request
resp_venues_ger <-
  GET(url = "https://app.ticketmaster.com/discovery/v2/venues.json?",
      query = list(
        apikey = api_key,    # provide secret API key to successfully call API
        countryCode = "DE",  # set countryCode as Germany
        locale = "*"         # use * to match all locales
      )
  )

# check status: if status code starts with a 2 the server received my request
status_code(resp_venues_ger)  # = 200 -> success

# extract the content from the response object using the content() function
# I use the non-error prone way: I specify as = "text" so that the content() function
# returns a character vector containing the JSON object...
content_venues_ger_json <- content(resp_venues_ger, as = "text")

# ... then I convert the JSON object into a R object by using the fromJSON() function
content_venues_ger <- fromJSON(content_venues_ger_json)
```

The list element `content_venues_ger` consists of three elements: `_embedded`, `_links` and `page`. The list element `_embedded` contains a data frame called `venues` which contains the variables we are interested in. More precisely, the data frame `venues` contains 20 observations of 19 variables. 
Of particular interest for this assignment is also the page element which contains information about the number of entries per page (stored in `size`), the number of total venues (stored in `totalElements`), the number of total Pages (stored in `totalPages`) and the current page number (stored in `number`). 

Lastly, the `name`, the `city`, the `postalCode` and `address`, as well as the `url` and the `longitude` and `latitude` of the venues from the `venues` part in the list element `_embedded` is extracted to a data frame. 

```{r ex3_dataframe}
# the relevant information is stored in the venues part of the list element "_embedded"
# i extract the information I need and create a data frame
df_venues <- data.frame(
  "name" = content_venues_ger$`_embedded`$venues$name, 
  "city" = content_venues_ger$`_embedded`$venues$city$name, 
  "postalCode" = content_venues_ger$`_embedded`$venues$postalCode, 
  "address" = content_venues_ger$`_embedded`$venues$address$line1,
  "url" = content_venues_ger$`_embedded`$venues$url,
  "longitude" = content_venues_ger$`_embedded`$venues$location$longitude,
  "latitude" = content_venues_ger$`_embedded`$venues$location$latitude
)

# show structure of data frame
# structure is similar to the structure of the task sheet
str(df_venues)
```

\

## Exercise 4: Interacting with the API - advanced

I take a closer look at the list element named `page` and recognize that my `GET()` request from Exercise 3 did not return *all* event locations in Germany. More precisely, it only returned the first 20 venues. In the following, I find out how many venues in Germany exist at all and on how many pages they are contained.

```{r ex4_page_result}
# how many results did my GET request yield?
result_per_page <- as.numeric(content_venues_ger$page$size)  # 20
result_per_page

# how many results are there in total?
n <- as.numeric(content_venues_ger$page$totalElements)  # 12238
n

# on how many pages are they?
pages <- as.numeric(content_venues_ger$page$totalPages)  # 612
pages

# on how many full pages? 
full_pages <- as.numeric(floor(n/result_per_page))  # 611
full_pages

# how many venues are on last page (page 612)?
results_last_page <- n - (full_pages * result_per_page)  # 18
results_last_page

# create empty data frame with right dimensions which is filled during loop 
# number of rows are the results per page times the number of full pages
n_rows <- result_per_page * full_pages

df_venues_all <- data.frame(
  "name" = character(n_rows), 
  "city" = character(n_rows), 
  "postalCode" = character(n_rows), 
  "address" = character(n_rows),
  "url" = character(n_rows), 
  "longitude" = character(n_rows),
  "latitude" = character(n_rows)
)

# important for the loop: first page starts with 0. Thus, the number of pages
# for the loop must be reduced by one. 
loop_pages <- full_pages - 1 

for (i in 0:loop_pages) {
  
  # perform GET request for each page
  resp_venues_ger_pagei <-
    GET(url = "https://app.ticketmaster.com/discovery/v2/venues.json?",
        query = list(
          countryCode = "DE",  # set countryCode as Germany
          apikey = api_key,    # provide secret API key to successfully call API
          page = i,            # page number
          locale = "*"         # use * to match all locales
        )
    )
  
  
  # extract content from response object
  content_json_pagei <- content(resp_venues_ger_pagei, as = "text")
  
  # convert JSON object in R object
  content_venues <- fromJSON(content_json_pagei)
  
  # create data frame for each page
  # sometimes location element is missing 
  # then missings for longitude  and latitude 
  if (is.null(content_venues$`_embedded`$venues$location$longitude)) {
    df_venues_pagei <- data.frame(
      "name" = content_venues$`_embedded`$venues$name, 
      "city" = content_venues$`_embedded`$venues$city$name, 
      "postalCode" = content_venues$`_embedded`$venues$postalCode, 
      "address" = content_venues$`_embedded`$venues$address$line1,
      "url" = content_venues$`_embedded`$venues$url,
      "longitude" = rep(NA, result_per_page),
      "latitude" = rep(NA, result_per_page)
    )
  } else {
    df_venues_pagei <- data.frame(
      "name" = content_venues$`_embedded`$venues$name, 
      "city" = content_venues$`_embedded`$venues$city$name, 
      "postalCode" = content_venues$`_embedded`$venues$postalCode, 
      "address" = content_venues$`_embedded`$venues$address$line1,
      "url" = content_venues$`_embedded`$venues$url,
      "longitude" = content_venues$`_embedded`$venues$location$longitude,
      "latitude" = content_venues$`_embedded`$venues$location$latitude
    )
  }

  # create index 
  j <- i + 1
  
  # calculate index to fill empty data frame
  index <- ((j - 1) * 20 + 1):(20 * j)
  
  # append data frame of each page to full data frame
  df_venues_all[index, ] <- df_venues_pagei
  
  # respect rate limit: 5 requests per second
  # with Sys.sleep(0.2) and Sys.sleep(0.25), I got an error message
  Sys.sleep(0.5)
  
}
```

\

## Exercise 5: Visualizing the extracted data

\

## Exercise 6: Event locations in other countries